A Survey of Scientific Workflow Management Systems

### 2014-04-25 paper.tex
minor

%
\paragraph{Pegasus/DAX} Pegasus \cite{deelman-peg} is a low-level distributed
computing framework that can map abstract workflows as DAGs to the concrete
underlying resources using intelligent\km{elaborate} and dynamic\km{elaborate} scheduling policies. A
Pegasus workflow is expressed in a simple XML-based language called DAX (DAG in
XML). DAX describes the logical workflow components, their inputs and outputs
and their links and dependencies in a Pegasus workflow. These kind of workflows
has been shown to enact optimally using Pegasus' smart memory and disk
management techniques. Pegasus manager buffers and maintains a fix-sized window
of executable tasks before accepting new tasks. Recent developments in Pegasus
enables it to run workflows on cloud
environments~\cite{peg-cloud}.\km{elaborate, does not seem to do GPU
computing}.

\paragraph{Wings/--} Wings is a Workflow system which does software choreography based on AI techniques~\cite{wings2013}. \km{elaborate}.

>>>>

%
\paragraph{Pegasus/DAX} Pegasus \cite{deelman-peg} is a low-level distributed
computing framework that can map abstract workflows as DAGs to the concrete
underlying resources using intelligent and dynamic\km{elaborate intelligent and dynamic} scheduling policies. A
Pegasus workflow is expressed in a simple XML-based language called DAX (DAG in
XML). DAX describes the logical workflow components, their inputs and outputs
and their links and dependencies in a Pegasus workflow. These kind of workflows
has been shown to enact optimally using Pegasus' smart memory and disk
management techniques. Pegasus manager buffers and maintains a fix-sized window
of executable tasks before accepting new tasks. Recent developments in Pegasus
enables it to run workflows on cloud
environments~\cite{peg-cloud}.\km{Pegasus does not seem to have GPU computing features}.

\paragraph{Wings/--} Wings is a Workflow system which does software
choreography based on AI techniques~\cite{wings2013}. \km{ToDo: expand}.
